Adaptive Disk Storage for Interaction Graphs

### 2014-07-19 docs/graph-adapt/main.tex
added ILP construction we use for expressing y and u constraints

% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize}  
    \sum_{q\in Q} \sum_{p=1}^{k}(16\cdot c_e(B) &+& 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    &+& \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q} \nonumber\\
\text{subject to}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} = 1\nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} q(a)\cdot x_{a,p} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  K\cdot y_{p,q} - \sum_{a\in A} q(a)\cdot x_{a,p}  \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q},
    && z_{a,p,q} - (x_{a,p} + y_{p,q}) \geq -1\nonumber\\
\forall_{p\in[1..k]},
    && \sum_{a\in A} x_{a,p} - u_p \geq 0 \nonumber\\
\forall_{p\in[1..k]},
    && K\cdot u_p - \sum_{a\in A} x_{a,p} \geq 0 \nonumber\\    
\Big(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\Big) &\cdot& \Big(\sum_{p=1}^{k} u_p -1\Big) \leq \alpha \nonumber
\end{eqnarray}

>>>>

% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize}  
    \sum_{q\in Q} \sum_{p=1}^{k} && (16\cdot c_e(B) + 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    &+& \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q} \nonumber\\
\text{subject to}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} = 1\nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} q(a)\cdot x_{a,p} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  K\cdot y_{p,q} - \sum_{a\in A} q(a)\cdot x_{a,p}  \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q},
    && z_{a,p,q} - (x_{a,p} + y_{p,q}) \geq -1\nonumber\\
\forall_{p\in[1..k]},
    && \sum_{a\in A} x_{a,p} - u_p \geq 0 \nonumber\\
\forall_{p\in[1..k]},
    && K\cdot u_p - \sum_{a\in A} x_{a,p} \geq 0 \nonumber\\    
 && \sum_{p=1}^{k} u_p -1 \leq \frac{\alpha}{
1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}
 } \nonumber
\end{eqnarray}

Here we use the following LP construction. Assume we have two variables,
$\beta_1$ and $\beta_2$, where $\beta_2\in[0,1]$ and $\beta_1\geq 0$. We want to
implement the following constraint: 
$$
\beta_2 = 
\begin{cases}
0 & \beta_1 = 0 \\
1 & \beta_1 \geq 0 
\end{cases}
$$

This could be expressed as a linear constraint as follows,  where $K$ is a
large constant guaranteed to be larger  that $\beta_1$ for practical purposes:
\begin{eqnarray}
\hspace{2cm}&& \beta_1 - \beta_2 \geq 0\nonumber\\
\hspace{2cm}&& K\cdot\beta_2 - \beta_1 \geq 0\nonumber
\end{eqnarray}

In our ILP formulation, we use this construction twice. The first use is shown
in the second and third constrants, where $\beta_1=\sum_{a\in A} q(a)\cdot
x_{a,p}$ and $\beta_2=y_{p,q}$. The second use is shown in the fifth and 
sixth constaints, where $\beta_1=\sum_{a\in A} x_{a,p}$ and $\beta_2=u_p$.
